Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-03-03 Scripts/Initial_Analysis.Rmd
Updated figures and estimated revenues

## Top fishing nations
Buble_data %>% 
  filter(log_value > Percentile_value$x & mean_yr < 2036) %>% 
  View()

>>>>

## Top fishing nations close to SDGs
Buble_data %>% 
  filter(log_value > Percentile_value$x & mean_yr < 2036) %>% 
  # View()
  group_by() %>% 
  summarise(sum(sum_value_bi),
            sum(n_taxa))

## All fishing nations close to SDGs
Buble_data %>% 
  filter(mean_yr < 2036) %>% 
  # nrow() # 76  coutries
  # View()
  group_by() %>% 
  summarise(sum(sum_value_bi),
            sum(n_taxa))

76/length(unique(Buble_data$sau_fishing_entity))
